MLExplain

### 2018-07-23 paper.tex
addressing more things

  \caption{Architecture of MLExplain}
  \label{fig:archi}
\end{figure*}

@@

Fortunately the web interface is very simple. It is composed of some auxiliary
JavaScript files, the main JavaScript file -- \texttt{navig-driver.js} --
containing the logic of the application and the corresponding HTML page. The
only modified file is \texttt{navig-driver.js}. The resulting tool can be tested
online.\footnote{\url{https://docteur-lalla.github.io/mlexplain/branch/master/driver.html}}

@@

>>>>

  \caption{Architecture of MLExplain}\label{fig:archi}
\end{figure*}

@@

Fortunately the web interface is very simple. It is composed of some auxiliary
JavaScript files, the main JavaScript file -- \texttt{navig-driver.js} --
containing the logic of the application and the corresponding HTML page. The
only modified file is \texttt{navig-driver.js}. The resulting tool can be tested
online\footnote{\url{https://docteur-lalla.github.io/mlexplain/branch/master/driver.html}}
and is shown in Figure~\ref{fig:mlexplain}. The top-left panel shows the
interpreted, here a simple eval function using GADTs, with the state of the
program depicted on the right. The bottom panel shows the
interpreter, with its state below. One can see that at this point the
\texttt{eval} identifier is being evaluated, with the values of \texttt{r},
\texttt{l}, and \texttt{b} shown on the right.

@@

\subsection{Design Choices}\label{subsec:design}

We now motivate our design choices. First, we use JavaScript because MLExplain
is a witness that JSExplain can easily be adapted to other languages, by
providing three components: an interpreter written in the subset of OCaml that
our compiler supports, a parser of the language, and a library to display OCaml
values. It would be possible to sever all links to the infrastructure provided
by JSExplain, but this would require significant work.

It is possible to use an existing debugger to explore how an interpreter works.
This is how we initially debugged our JavaScript interpreter and this was the
motivation to start working on JSExplain. Indeed, our interpreter is written as
a purely functional set of recursive functions that extensively use monadic
operations implemented in continuation passing style. It is difficult to
correctly navigate such functions, as stepping over a continuation means
reaching the end of the program. One thus has to be aware of whether a function
call is a continuation or a usual function. In addition, we did not find an easy
way to display the state of the interpreted program, even when relying on the
use of fixed names for the term, the state, and the context.
